Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2022-05-06 article/draft.tex
ignore screenshots

{\bf A need for more complete data.} 
When Facebook, Twitter or YouTube intervene by suspending an account, the data can no longer be accessed via scraping or via the official APIs (Twitter, YouTube, CrowdTangle) for the purposes of scientific research. 
This hampers the investigation of how platforms moderate content. 
To further illustrate this point, the original list of YouTube videos with failed fact-checks (summarized in Figure \ref{youtube_panel_proportions}), had over $200$ YouTube videos available in March $2021$. 
However, by June $2021$, thirty videos had disappeared from the YouTube API for policy violation. 
Similarly, in a related research project, Th\'{e}ro and Vincent (2020)~\cite{therovincent} searched on CrowdTangle for $94$ public accounts sharing specific content associated with misinformation in November $2020$. 
They tried to collect the posts from those $94$ pages in January $2021$, to only discover that $11$ pages had disappeared from the CrowdTangle API.
It is of course not surprising that platforms are regulating their content, sometimes by removing it. 
Nevertheless, researchers' work could be simplified, if metadata for content posted by removed accounts could still be accessible via the APIs.

>>>>

{\bf A need for more complete data.} 
When Facebook, Twitter or YouTube intervene by suspending an account, the data can no longer be accessed via scraping or via the official APIs (Twitter, YouTube, CrowdTangle) for the purposes of scientific research. 
This hampers the investigation of how platforms moderate content. 
To further illustrate this point, the original list of YouTube videos with failed fact-checks (summarized in Figure \ref{youtube_panel_proportions}), had over $200$ YouTube videos available in March $2021$. 
However, by June $2021$, thirty videos had disappeared from the YouTube API for policy violation. 
Similarly, in a related research project, Th\'{e}ro and Vincent (2020)~\cite{therovincent} searched on CrowdTangle for $94$ public accounts sharing specific content associated with misinformation in November $2020$. 
They tried to collect the posts from those $94$ pages in January $2021$, to only discover that $11$ pages had disappeared from the CrowdTangle API.
Researchers' work could be simplified, if metadata for content posted by removed accounts could still be accessible via the APIs.
